---
title: "Species_quantification"
output:
  html_document: default
  pdf_document: default
---

## Loading packages

```{r setup}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(ggstatsplot)
library(multimode)
library(grid)
library(ggpubr)
library("Rcpp")
library("readxl")
library(rstatix) 
library(ggprism)
library(patchwork)
library(emmeans)
library(magrittr)
```

## set directory (home/office) and upload files
## Create the environment and directories
```{r}
#Set working dir location location 
print("Main Folder")
(WD <- dirname(rstudioapi::getSourceEditorContext()$path)) 
if (!is.null(WD)) setwd(WD) 

#Folder to export results data to
species=basename(WD) ## This has to be adjusted for each Species
figDir="Figures"
dataDir="Data"

#Check if folder exist, if else make it
## Figure Directory
print("Figure Directory exist")
ifelse(!dir.exists(file.path(WD, figDir)), 
       dir.create(file.path(WD, figDir)), T)
print("Data Directory exist")
ifelse(!dir.exists(file.path(WD, dataDir)), 
       dir.create(file.path(WD, dataDir)), T)


cilia_H <- read.delim("results_cilia_H.txt", sep="", header=T,
                      dec = ",")

GFP_Human <- read.delim("results_infection_H.txt", sep="", header=T,
                        dec = ",")

cilia_P <- read.delim("results_cilia_P.txt", sep="", header=T,
                      dec = ",")

GFP_Porcine <- read.delim("results_infection_P.txt", sep="", header=T,
                        dec = ",")

cilia_B <- read.delim("results_cilia_bovine_corrected.txt", sep="", header=T,
                      dec = ",")

GFP_Bovine <- read.delim("results_infection_bovine_corrected.txt", sep="", header=T,
                        dec = ",")


```

## put Cy5 and GFP tables together

```{r}
#for Human
colnames(GFP_Human)[4] <- c("GFP_mean_intensity")
colnames(cilia_H)[4] <- c("Cy5_mean_intensity")

Human <- cbind.data.frame(cilia_H, GFP_Human[4])

#for pig
colnames(GFP_Porcine)[4] <- c("GFP_mean_intensity")
colnames(cilia_P)[4] <- c("Cy5_mean_intensity")

Porcine <- cbind.data.frame(cilia_P, GFP_Porcine[4])

#for bovine

colnames(GFP_Bovine)[4] <- c("GFP_mean_intensity")
colnames(cilia_B)[4] <- c("Cy5_mean_intensity")

Bovine <- cbind.data.frame(cilia_B, GFP_Bovine[4])
```

## Relabel bovine table to fit Human and porcine ones

```{r}
colnames(Bovine)[which(names(Bovine) == "replicate")] <- "donor"

colnames(Bovine)[which(names(Bovine) == "experiment")] <- "infection"

Bovine <- Bovine %>% 
  relocate(channel, .after = image)
```

## combine all species info in one single table
```{r}
Species <- rbind(Human, Porcine, Bovine)

Species$Cy5_mean_intensity <- as.numeric(Species$Cy5_mean_intensity)
Species$GFP_mean_intensity <- as.numeric(Species$GFP_mean_intensity)

#set area,  cy5 and GFP values to log10
Species <- Species %>%
  dplyr::mutate(area = log10(area), Cy5_mean_intensity = log10(Cy5_mean_intensity), 
         GFP_mean_intensity = log10(GFP_mean_intensity))
```

#clean data from too small cells

```{r}
Quantile <- Species %>%
  group_by(species) %>%
  summarise(quantile = quantile(area, probs=c(.25, .75), na.rm = FALSE), IQR = IQR(area))

Species_filtered <- Species %>%
  group_by(species) %>%
  subset(area > ((Quantile$quantile - 1.5*Quantile$IQR) & area < (Quantile$quantile + 1.5*Quantile$IQR)))

#table(Species$species)
#table(Species_filtered$species)
```
#create a new column for infected/non-infected cells: 1=infected, 0=un-infected
```{r}

Mock_GFP <- Species_filtered %>%
  group_by(species, donor, temperature, virus) %>%
  subset(infection == c("MC", "MD")) %>%
  summarise(mean_GFP = mean(GFP_mean_intensity), sd_GFP = sd(GFP_mean_intensity), mean_sd = (mean_GFP + 3*sd_GFP))

Species_GFP <- Species_filtered %>%
    left_join(Mock_GFP) %>% 
    mutate(Cy5_mean_intensity=Cy5_mean_intensity, GFP_mean_intensity=GFP_mean_intensity,
                  infected_cell = ifelse(GFP_mean_intensity > mean_sd, 1, 0))

Human <- subset(Species_GFP, species==c("H")) 

Porcine <- subset(Species_GFP, species ==c("P"))

Bovine <- subset(Species_GFP, species ==c("B"))


Species = rbind(Human, Porcine, Bovine)

```

#ciliated vs non ciliated
```{r, warning=FALSE}

Species$Cy5_mean_intensity <- as.numeric(Species$Cy5_mean_intensity)
Species$GFP_mean_intensity <- as.numeric(Species$GFP_mean_intensity)

df <- subset(Species, select = -c( perimeter, feret_diameter_max : file, channel, mean_GFP:mean_sd))

df <- df %>%
  group_by(species, donor, temperature, virus, infection, image) %>%
  mutate(cilia = Cy5_mean_intensity)


#find range non-ciliated vs ciliated (using multimode package)

df <- df %>%
  group_by(species, donor, temperature, virus, infection, image) %>%
  mutate(loc = (locmodes(cilia, mod0 = 2, display = FALSE))$locations[2]) 

Species <- df %>%
  group_by(species, donor, temperature, virus, infection, image, loc, min)%>%
  mutate(ciliated_cell = ifelse(cilia > loc , 1, 0))


```

#percentage of ciliated cells in mock samples
```{r}
Mock_samples <- subset(Species, infection==c("MC", "MD")) %>%
  group_by(species, donor) %>%
  summarise(cells = length(label))

Mock_ciliated_samples <- subset(Species, infection==c("MC", "MD")) %>%
  subset(ciliated_cell==c("1")) %>%
  group_by(species, donor) %>%
  summarise(cilia=length(label))

ciliated_ratio <- Mock_ciliated_samples %>%
  left_join(Mock_samples)%>%
  group_by(species, donor)%>%
    summarise(ratio = cilia/cells)

ciliated_mean <- ciliated_ratio %>%
  group_by(species)%>%
    summarise(ratio, mean_cilia = mean(ratio), sem=sd(ratio)/sqrt(length(ratio)), 
            ymin_sem = mean_cilia-sem,
            ymax_sem = mean_cilia+sem,
            sd=sd(ratio), 
            ymin_sd=mean_cilia-sd, ymax_sd=mean_cilia+sd)


# New facet label names for species
species.labs <- c("Human", "Porcine", "Bovine")
names(species.labs) <- c("H", "P", "B")


mock_cilia_percentage <- ggplot(ciliated_mean, aes(x=species, y=mean_cilia), labeller=species.labs)+
  geom_bar(stat = "identity", colour = "black", size=0.7, fill='#d73027')+
  geom_errorbar(aes(ymin=ymin_sd, ymax=ymax_sd), size=0.7, width = 0.4)+ 
  theme_bw()+
  scale_x_discrete(limits = c("H", "P", "B"),
                   labels = c("Human", "Porcine", "Bovine"))+
  scale_y_continuous(limits =c(0,1), labels = scales::percent_format(accuracy = 1))+
  xlab("Temperature")+
  ylab("Percentage of ciliated cells")+
  theme(axis.title.x = element_text(size=28))+
  theme(axis.title.y = element_text(size=28))+
  theme(axis.text.x = element_text(size=26))+
  theme(axis.text.y = element_text(size=26))

mock_cilia_percentage


```

#check for significance:

```{r}
ciliated_mean$species <- as.factor(ciliated_mean$species)
ciliated_mean$ratio <- as.numeric(ciliated_mean$ratio)

ciliated_ratio <- ciliated_ratio %>%
  ungroup()

#normality test
qqPlot(ciliated_ratio$ratio)
shapiro.test(ciliated_ratio$ratio)

#t.test
pwc1 <- ciliated_ratio %>%
  pairwise_t_test(ratio ~ species, paired = T) %>%
  add_significance() %>%
  add_xy_position(x="species", dodge = 0.9)

pwc1

mock_cilia_percentage_sign <- ggplot(ciliated_mean, aes(x=species, y=ratio), labeller=species.labs)+
  geom_bar(stat = "summary",  colour = "black", size=0.7, fill='#d73027')+
  geom_errorbar(aes(ymin=ymin_sd, ymax=ymax_sd), size=0.7, width = 0.4)+ 
  theme_bw()+
  scale_x_discrete(limits = c("H", "P", "B"),
                   labels = c("Human", "Porcine", "Bovine"))+
  stat_pvalue_manual(pwc1, size = 10, hide.ns = F,bracket.nudge.y = 0.1, step.increase=0.08) +
  scale_y_continuous(breaks = seq(0, 1, 0.2), limits =c(0,1.2), labels = scales::percent_format(accuracy = 1))+
  xlab("Temperature")+
  ylab("Percentage of ciliated cells")+
  theme(axis.title.x = element_text(size=37))+
  theme(axis.title.y = element_text(size=37))+
  theme(axis.text.x = element_text(size=32))+
  theme(axis.text.y = element_text(size=32))

mock_cilia_percentage_sign

 
```



# cell count

```{r}
Species_IS <- subset(Species, infection==c("C", "D")) 

Species_IS$image <- as.numeric(Species_IS$image)

#cell count per donor and per image (infected and non infected)
df <- Species_IS %>%
  group_by(species, temperature, virus, donor, infected_cell, image) %>%
  summarise(cell_image = mean((length(label))))%>%
  ungroup %>%
  complete(nesting(species, temperature, virus, donor, infected_cell, image),
           fill = list(cell_image = 0))


#cell count per donor (infected and non infected)

df2 <- df%>%
  group_by(species, temperature, virus, donor, infected_cell) %>%
  summarise(cell_count_donor = mean(cell_image)) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus, donor),
           nesting(infected_cell),
           fill = list(cell_count_donor = 0))

#mean cell count (infected and non infected)

all_cells <- df2%>%
  group_by(species, temperature, virus, infected_cell) %>%
  summarise(cell_count_mean = mean(cell_count_donor), sd=sd(cell_count_donor), 
            sem=sd(cell_count_donor)/sqrt(length(cell_count_donor)), 
            ymin_sd = cell_count_mean-sd,
            ymax_sd = cell_count_mean+sd,
            ymin_sem = cell_count_mean - sem,
            ymax_sem = cell_count_mean + sem) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus),
           nesting(infected_cell),
           fill = list(cell_count_mean = 0))

  
all_cells$species <- factor(all_cells$species, levels = c("H", "P", "B"))

all_cells$species <- as.factor(all_cells$species)
all_cells$infected_cell <- as.factor(all_cells$infected_cell)
all_cells$virus <- as.factor(all_cells$virus)
all_cells$temperature <- as.factor(all_cells$temperature)

all_cells$cell_count_mean <- as.numeric(all_cells$cell_count_mean)
all_cells$sd <- as.numeric(all_cells$sd)
all_cells$sem <- as.numeric(all_cells$sem)
all_cells$ymin_sd <- as.numeric(all_cells$ymin_sd)
all_cells$ymax_sd <- as.numeric(all_cells$ymax_sd)
all_cells$ymin_sem <- as.numeric(all_cells$ymin_sem)
all_cells$ymax_sem <- as.numeric(all_cells$ymax_sem)
all_cells$temperature <- paste0(all_cells$temperature, "째C") #adding Temperature symbol to variable


# New facet label names for species
species.labs <- c("Human", "Porcine", "Bovine")
names(species.labs) <- c("H", "P", "B")


#as dodge plot
ggplot(all_cells, aes(x=temperature, y=cell_count_mean, fill=infected_cell))+
  facet_wrap(species~virus, scales = "free", ncol=2, nrow=3, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  ylab("Mean cell count")+
  labs(title = "Total cell count")+
  ggeasy::easy_center_title()

Species_ICV <- subset(all_cells, virus==c("ICV")) 

total_cell_count_ICV <- ggplot(Species_ICV, aes(x=temperature, y=cell_count_mean, fill=infected_cell))+
  facet_wrap(~species, scales = "free", ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  ylab("Mean cell count")+
  labs(title = "Total cell count")+
  ggeasy::easy_center_title()+
  theme(axis.title.x = element_text(size=22))+
  theme(axis.title.y = element_text(size=22))+
  theme(axis.text.x = element_text(size=20, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=20))+
  theme(legend.text = element_text(size=20))+
  theme(strip.text.x = element_text(size = 20))


total_cell_count_ICV


Species_IDV <- subset(all_cells, virus==c("IDV")) 

total_cell_count_IDV <- ggplot(Species_IDV, aes(x=temperature, y=cell_count_mean, fill=infected_cell))+
  facet_wrap(~species, scales = "free", ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  ylab("Mean cell count")+
  labs(title = "Total cell count")+
  ggeasy::easy_center_title()+    
  theme(axis.title.x = element_text(size=22))+
  theme(axis.title.y = element_text(size=22))+
  theme(axis.text.x = element_text(size=20, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=20))+
  theme(legend.text = element_text(size=20))+
  theme(strip.text.x = element_text(size = 20))


total_cell_count_IDV

```
# total cell count in cells/mm2

```{r}
#make table with information of image sizes

Norm_df <- data.frame(species=c("H", "P", "B"), magnification = c("20x", "20x", "40x"), 
                      HandW = c(694, 694, 153.6))

#um2=area of image, mm2= area of image in mm2

Norm_df <- Norm_df %>%
  left_join(Norm_df)%>%
  mutate(species, magnification, HandW, um2 = (Norm_df$HandW)^2, mm2=um2/1e6) 

#normalize cell count in cells/mm2
normalization_cells <- df2 %>%
  group_by(species) %>%
  left_join(Norm_df)%>%
  mutate(cell_mm2 = (cell_count_donor/mm2))

#mean cell count/m2 (infected and non infected)

cellsarea <- normalization_cells%>%
  group_by(species, temperature, virus, infected_cell) %>%
  summarise(cell_area_mean = mean(cell_mm2), sd=sd(cell_mm2), 
            sem=sd(cell_mm2)/sqrt(length(cell_mm2)), 
            ymin_sd = cell_area_mean-sd,
            ymax_sd = cell_area_mean+sd,
            ymin_sem = cell_area_mean - sem,
            ymax_sem = cell_area_mean + sem) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus),
           nesting(infected_cell),
           fill = list(cell_area_mean = 0))

#display in graph
cellsarea$cell_area_mean <- as.numeric(cellsarea$cell_area_mean)

cellsarea$species <- factor(cellsarea$species, levels = c("H", "P", "B"))

cellsarea$species <- as.factor(cellsarea$species)
cellsarea$infected_cell <- as.factor(cellsarea$infected_cell)
cellsarea$virus <- as.factor(cellsarea$virus)
cellsarea$temperature <- as.factor(cellsarea$temperature)
cellsarea$sd <- as.numeric(cellsarea$sd)
cellsarea$sem <- as.numeric(cellsarea$sem)
cellsarea$ymin_sd <- as.numeric(cellsarea$ymin_sd)
cellsarea$ymax_sd <- as.numeric(cellsarea$ymax_sd)
cellsarea$ymin_sem <- as.numeric(cellsarea$ymin_sem)
cellsarea$ymax_sem <- as.numeric(cellsarea$ymax_sem)
cellsarea$temperature <- paste0(cellsarea$temperature, "째C") #adding Temperature symbol to variable


#as dodge plot 
plot_cellsarea <- ggplot(cellsarea, aes(x=temperature, y=cell_area_mean, fill=infected_cell))+
  facet_wrap(species~virus, scales = "free", ncol=2, nrow=3, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  ylab("Number of cells per mm2")+
  #labs(title = "Total cell count")+
  ggeasy::easy_center_title()

plot_cellsarea

#separate for ICV and IDV

ICV_cells_area <- subset(cellsarea, virus==c("ICV"))

ICV_cells_area <- ggplot(ICV_cells_area, aes(x=temperature, y=cell_area_mean, fill=infected_cell))+
  facet_wrap(~species, scales = "free", ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  theme_bw()+
  ylab("Number of cells per mm2")+
  labs(title = "ICV")+
  ggeasy::easy_center_title()+
  theme(title = element_text(size=26))+
  theme(axis.title.x = element_text(size=26))+
  theme(axis.title.y = element_text(size=26))+
  theme(axis.text.x = element_text(size=24, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=24))+
  theme(legend.text = element_text(size=24))+
  theme(strip.text.x = element_text(size = 24))

ICV_cells_area

IDV_cells_area <- subset(cellsarea, virus==c("IDV"))

IDV_cells_area <- ggplot(IDV_cells_area, aes(x=temperature, y=cell_area_mean, fill=infected_cell))+
  facet_wrap(~species, scales = "free", ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "dodge",  stat = "identity", colour = "black", size=0.2)+
  geom_errorbar(aes(ymin = ymin_sd,
                    ymax = ymax_sd), width=0.2, position=position_dodge(width = 0.9), stat = "identity", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-infected cells", "Infected cells"))+
  theme_bw()+
  ylab(NULL)+
  labs(title = "IDV")+
  ggeasy::easy_center_title()+
  theme(title = element_text(size=26))+
  theme(axis.title.x = element_text(size=26))+
  theme(axis.title.y = element_text(size=26))+
  theme(axis.text.x = element_text(size=24, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=24))+
  theme(legend.text = element_text(size=24))+
  theme(strip.text.x = element_text(size = 24))

IDV_cells_area

```
#check significance
```{r}
#normality test
uninfected <- normalization_cells%>%
  subset(infected_cell=="0")%>%
  group_by(species)%>%
  shapiro_test(cell_mm2)

#t.test uninfected vs infected
pwc1 <- normalization_cells %>%
  group_by(species, virus, temperature)%>%
  pairwise_t_test(cell_mm2 ~ infected_cell, paired = T) %>%
  add_significance() %>%
  add_xy_position(x="temperature", dodge = 0.9)
pwc1

#t.test  infected panels 33 vs 37째C
pwc2 <- normalization_cells %>%
  subset(infected_cell=="1")%>%
  group_by(species, virus)%>%
  pairwise_t_test(cell_mm2 ~ temperature, paired = T) %>%
  add_significance() %>%
  add_xy_position(x="temperature", dodge = 0.9)
pwc2

```


#graph infected cells only

```{r}

a <- Species_IS %>%
  subset(infected_cell==c("1"), .preserve=TRUE)%>%
  group_by(species, temperature, virus, donor, ciliated_cell, image) %>%
  summarise(cell_image = mean((length(label)))) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus, donor, image),
           nesting(ciliated_cell),
           fill = list(ciliated_cell = 0, cell_image = 0))

b <- a %>%
  group_by(species, temperature, virus, donor, ciliated_cell) %>%
  summarise(donor_cellcount = mean(cell_image)) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus),
           nesting(ciliated_cell),
           fill = list(ciliated_cell = 0, donor_cellcount = 0))

infected_cells <- b %>%
  group_by(species, temperature, virus, ciliated_cell) %>%
  summarise(mean_cellcount = mean(donor_cellcount)) %>%
  ungroup %>%
  complete(nesting(species, temperature, virus),
           nesting(ciliated_cell),
           fill = list(ciliated_cell = 0, mean_cellcount = 0))

infected_cells$species <- factor(infected_cells$species, levels=c("H", "P", "B"))
 
infected_cells$species <- as.factor(infected_cells$species)
infected_cells$ciliated_cell <- as.factor(infected_cells$ciliated_cell)
infected_cells$virus <- as.factor(infected_cells$virus)
infected_cells$cell_count_mean <- as.numeric(infected_cells$mean_cellcount)

infected_cells$temperature <- as.factor(infected_cells$temperature)
infected_cells$temperature <- paste0(infected_cells$temperature, "째C") #adding Temperature symbol to variable


#percentage 
ggplot(infected_cells, aes(x=temperature, y=mean_cellcount, fill=ciliated_cell))+
  facet_wrap(species~virus, ncol=2, nrow=3, labeller = labeller(species = species.labs))+
  geom_bar(position = "fill",stat="identity", colour = "black", size=0.2)+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-ciliated cells", "Ciliated cells"))+
  ylab("Percentage cell count")+
  labs(title = "Infected cells")+
  ggeasy::easy_center_title()


#Separate ICV from IDV

#ICV graph

Species_ICV_infected <- subset(infected_cells, virus==c("ICV")) 
 
#percentage
ICV_percentage <- ggplot(Species_ICV_infected, aes(x=temperature, y=cell_count_mean, fill=ciliated_cell))+
  facet_wrap(~species, ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "fill",stat="identity", colour = "black", size=0.2)+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-ciliated cells", "Ciliated cells"))+
  theme_bw()+
  ylab("Percentage cell count")+
  #labs(title = "ICV infected cells")+
  ggeasy::easy_center_title()+
  theme(axis.title.x = element_text(size=26))+
  theme(axis.title.y = element_text(size=26))+
  theme(axis.text.x = element_text(size=24, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=24))+
  theme(legend.text = element_text(size=24))+
  theme(strip.text.x = element_text(size = 24))

ICV_percentage

#IDV graph


Species_IDV_infected <- subset(infected_cells, virus==c("IDV")) 

#percentage
IDV_percentage <- ggplot(Species_IDV_infected, aes(x=temperature, y=cell_count_mean, fill=ciliated_cell))+
  facet_wrap(~species, ncol=3, nrow=1, labeller = labeller(species = species.labs))+
  geom_bar(position = "fill",stat="identity", colour = "black", size=0.2)+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  scale_fill_manual(name = NULL, values = c("#fddbc7","#d73027"), breaks = c("0", "1"), labels = c("Non-ciliated cells", "Ciliated cells"))+
  theme_bw()+
  ylab(NULL)+
  #labs(title = "IDV infected cells")+
  ggeasy::easy_center_title()+
  theme(axis.title.x = element_text(size=26))+
  theme(axis.title.y = element_text(size=26))+
  theme(axis.text.x = element_text(size=24, angle = 45, vjust = 1, hjust=1))+
  theme(axis.text.y = element_text(size=24))+
  theme(legend.text = element_text(size=24))+
  theme(strip.text.x = element_text(size = 24))

IDV_percentage
 
```
